Lossy compression of DNA sequencing quality data

### 2015-05-13 manuscript/q-compression.tex
removed extraneous word

Although we focus only on two bins in this work, a greater number of
bins can be used in practice, albeit with a higher cost in memory
requirement.  For example, an additional third bin, thus giving bins
of good, bad, and intermediate, could be used for base qualities near
the border between bins in the 2-bin encoding. Additional bins beyond
two, and their resulting compressibility and effect on downstream
analyses, are not considered here.

>>>>

Although we focus only on two bins in this work, a greater number of
bins can be used in practice, albeit with a higher cost in memory
requirement.  For example, an additional bin, thus giving bins
of good, bad, and intermediate, could be used for base qualities near
the border between bins in the 2-bin encoding. Additional bins beyond
two, and their resulting compressibility and effect on downstream
analyses, are not considered here.
